### 2012-06-20 intention motor representation with corrado sinigaglia/intention and motor action.ppr.corrected.tex
proofing done

A further conjecture is that whenever there is a non-accidental match between the contents of intentions and of motor representations, this is due at least in part to deferential action concepts. The plausibility of this conjecture rests in part on the absence of any other viable full solution to the interface problem, and of course we do not claim to have shown that no alternatives exists. If the conjecture is right, if there is no way of fully solving the interface problem other than by means of deferential action concepts, then concepts which refer by deferring to motor representations are what tie explicit practical reasoning to motor processes.

@@

On this view experience of acting plays a novel role. Experiences made possible by motor representation, such as those associated with phenomenologically action-like imagination and those associated with actual action, are arguably necessary for there to be concepts which are constituents of intentions and refer to actions by deferring to motor representations. But if, as we conjecture, such deference is necessary for intentions to properly and reliably result in bodily movements, it may turn out that intending to act in the world depends on experiences which are made possible by motor representation. Much as on some views thought about objects depends on perceptual experience \citep[e.g.][]{Campbell:2002ge}, so also intending actions may depend on motor experience.%
\footnote{
Heartfelt thanks to Chiara Brozzo, Silvano Zipoli Caiani, Naomi Eilan, Vittorio Gallese, Francesco Guala, \'Elisabeth Pacherie and Natalie Sebanz.  Corado Sinigaglia was supported by EU grant TESIS, a Fellowship from the Institute of Philosophy (University of London) and a Fellowship from the Center for the Epistemology of Cognitive Sciences, Ecole Normale Superiéure de Lyon.
}

>>>>

A further conjecture is that whenever there is a non-accidental match between the contents of intentions and of motor representations, this is due at least in part to deferential action concepts. 
The plausibility of this conjecture rests in part on the absence of any other viable full solution to the interface problem, and of course we do not claim to have shown that no alternatives exist. 
If the conjecture is right, then concepts which refer by deferring to motor representations are what tie explicit practical reasoning to motor processes.

@@

On this view experience of acting plays a novel role. Experiences made possible by motor representation, such as those associated with phenomenologically action-like imagination and those associated with actual action, are arguably necessary for there to be concepts which are constituents of intentions and refer to actions by deferring to motor representations. But if, as we conjecture, such deference is necessary for intentions to properly and reliably result in bodily movements, it may turn out that intending to act in the world depends on experiences which are made possible by motor representation. Much as on some views thought about objects depends on perceptual experience \citep[e.g.][]{Campbell:2002ge}, so also intending actions may depend on motor experience.%
\footnote{
Heartfelt thanks to Gabriella Bottini, Chiara Brozzo, Silvano Zipoli Caiani, Naomi Eilan, Vittorio Gallese, Francesco Guala, \'Elisabeth Pacherie, Natalie Sebanz and an anonymous referee.  Corado Sinigaglia was supported by EU grant TESIS, a Fellowship from the Institute of Philosophy (University of London) and a Fellowship from the Center for the Epistemology of Cognitive Sciences, Ecole Normale Superiéure de Lyon.
}
